---
title: "Matthew Flanagan - Chapter 4 - Dissertation"
output: html_notebook
---


```{r}
#load packages
library(lavaan)
library(readxl)
library(tidyverse)

#get the TDQI data
d1 <- read_excel("Allentown.xlsx")
d2 <- read_excel("Avon_Grove.xlsx")
d3 <- read_excel("Butler.xlsx")
d4 <- read_excel("Canon_McMillan.xlsx")
d5 <- read_excel("East_Lycoming.xlsx")
d6 <- read_excel("Lebanon.xlsx")
d7 <- read_excel("Mountain_View.xlsx")
d8 <- read_excel("PA_Virtual_Charter.xlsx")
d9 <- read_excel("Plum_Borough.xlsx")
d10 <- read_excel("Southwestern.xlsx")
d11 <- read_excel("Union_Area.xlsx")

```

```{r}
#make a column index for reference, change df as needed to update / modify the index list as cleaning is being completed. Makes de-bugging easier. Not Required. 
column_indexY <- data.frame(colnames(d8Y)) #youth
column_indexF <- data.frame(colnames(d8F)) #parents with 1 young person with a disability
column_indexFm <- data.frame(colnames(d8Fm)) #parents with more than 1 young person with a disability
column_indexS <- data.frame(colnames(d8S)) #transition stakeholders

```


Process d1 through chunks 1 through 6. Then, find and replace "d1" chunks 1 through 5 below. Run the modified chunks to clean each site file EXCEPT for d8, which is a charter. Charter school data is structured slightly different and needs to be cleaned separately. See chunks 7 through 12 for cleaning charter data.

```{r}
#CHUNK 1

#Rename role, age, gender, school, race
d11 <- d11 %>% rename(Role = Q1) %>% 
  rename(Age = Q2) %>% rename(Gender = Q3) %>% 
  rename(School = Q5) %>% rename(Race_Eth = Q4)

#remove first row acting as question name which was added by Qualtrics out-dated export functionality.
d11 <- d11[-c(1),]
```  

```{r}
#CHUNK 2

#Cleaning Youth Responses
d11Y <- d11 %>% filter(Role =="I'm a Young Person") %>% #filter out just youth responses
  filter(Finished=="True") %>% #only complete responses
  select(-c(77:698)) %>% #remove all fields from the family and stakeholder survey questions
  select(-c(85:93)) %>% #remove unneeded embedded data from Qualtrics
  select(-c(81:84)) %>% #remove unneeded embedded demographic data from Qualtrics. Not accurate. Already have fields.
  select(-c(75:76)) %>% #remove written youth responses
  select (-c(1:10)) %>% #remove embedded survey data from Qualtrics (date, time, etc.)
  mutate(Q773 = Q773 %>% str_replace_all(c("Some\r\n" = "Some",
                                  "A lot\r\n" = "A lot",
                                  "Not at all\r\n" = "Not at all",
                                  "Some" = "Some",
                                  "A lot" = "A lot",
                                  "Not at all" = "Not at all")))
  d11Y <- d11Y %>% select(-c(6:10)) #remove unneeded write-ins for youth demographics
d11Y <- d11Y %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Don't Know / Doesn't Relate to Me" = 0,
            )))

colnames(d11Y)[6:59] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
```

```{r}
#CHUNK 3

#Cleaning Parent Responses - one young person
d11F <- d11 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:76)) %>% #remove youth response fields
  select(-c(1:151)) %>% #remove stakeholder response fields
  select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics
  select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(60:419)) %>% #remove fields for parents responding about more than one young person
  select(-c(60:77)) %>% #remove unneeded embedded data pt 1
  select(-c(64:76)) %>% #remove unneeded embedded data pt 2
  filter(Q166 == "I want to share about one young person")

d11F <- d11F %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable" = 0,
            )))

colnames(d11F)[6:59] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
d11F$Role <- as.character("I'm a Parent / Legal Guardian")

```

```{r}
#CHUNK 4

#Cleaning Parent Responses - multiple young people
d11Fm <- d11 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:76)) %>% #remove youth response fields
  select(-c(1:151)) %>% #remove stakeholder response fields
  select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics from single youth parents
  select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(1:59)) #remove item fields for single youth parents

d11Fm <- d11Fm %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable" = 0,
            )))

```

```{r}
#CHUNK 5

#Cleaning Stakeholder Responses
d11S <- d11 %>% filter(Role == "I'm a Transition Stakeholder") %>%
  filter(Finished=="True") %>% #only complete response
  select(-c(1:10)) %>% #remove embedded demographic data fields from Qualtrics
  select(-c(2:66)) %>% #remove youth fields
  select(-c(3,4,5,8)) %>% #remove write-in fields and unneeded demo fields for stakeholders
  select(-c(17,18,35,36,47,48,61,62,75,76,93,94,110,111,133,134,147:150)) %>% #remove stakeholder written responses
  select(-c(131:599)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(135:147)) #remove embedded scores as well as other unneeded embedded fields

d11S <- d11S %>% mutate_at(vars(5:8,17:24,33,34,43:46,55:58,67:74,83:89,98:110,119:122), #re-code all sqi ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable"=0,
              "Not Applicable"=0
            )))
colnames(d11S)[5:8] <- c(paste0("SQI",1:4)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[17:24] <- c(paste0("SQI",5:12)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[33:34] <- c(paste0("SQI",13:14)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[43:46] <- c(paste0("SQI",15:18)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[55:58] <- c(paste0("SQI",19:22)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[67:74] <- c(paste0("SQI",23:30)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[83:89] <- c(paste0("SQI",31:37)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[98:110] <- c(paste0("SQI",38:50)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[119:122] <- c(paste0("SQI",51:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.

d11S <- d11S %>% mutate_at(vars(9:11,25:27,35:37,47:49,59:61,75:77,90:92,111:113,123:125), #re-code all ADAPT ratings from string to numerical
            ~as.numeric(recode(.,
              "Limited Adaptation (2)"=2,
              "Full Adaptation (4)"=4,
              "No Adaptation (1)"=1,
              "Partial Adaptation (3)"=3,
              "Not Applicable"=0,
              "Not applicable"=0
            )))

d11S <- d11S %>% mutate_at(vars(12:14,28:30,38:40,50:52,62:64,78:80,93:95,114:116,126:128), #re-code all ACCESS ratings from string to numerical
            ~as.numeric(recode(.,
              "Limited Access (2)"=2,
              "Full Access (4)"=4,
              "No Access (1)"=1,
              "Partial Access (3)"=3,
              "Not Applicable"=0,
              "Not applicable"=0
            )))

d11S <- d11S %>% select(-c(15,16,31,32,41,42,53,54,65,66,81,82,96,97,117,118,129,130)) #remove resource level and effectiveness ratings. They are not used in the model

```

```{r}
#CHUNK 6

#union youth, family and stakeholder tables
d11join <- full_join(d11Y,d11F) #youth and families
d11final <- full_join(d11join,d11S) #join with stakeholders
rm(d11join,d11,d11F,d11S,d11Y)

```


Chunks 7 through 12 below are used ONLY for cleaning the charter data (d8)

```{r}
#CHUNK 7

#Rename role, age, gender, school, race
d8 <- d8 %>% rename(Role = Q1) %>% 
  rename(Age = Q2) %>% rename(Gender = Q3) %>% 
  rename(School = Q5) %>% rename(Race_Eth = Q4)

#remove first row acting as question name which was added by Qualtrics out-dated export functionality.
d8 <- d8[-c(1),]
```  

```{r}
#CHUNK 8

#Cleaning Youth Responses
d8Y <- d8 %>% filter(Role =="I'm a Young Person") %>% #filter out just youth responses
  filter(Finished=="True") %>% #only complete responses
  select(-c(75:696)) %>% #remove all fields from the family and stakeholder survey questions
  select(-c(75:83)) %>% #remove embedded scores
  select(-c(78:85)) %>% #remove fields relevant to families with more than one young person with a disability pt1
  select(-c(79:80)) %>% #remove fields relevant to families with more than one young person with a disability pt2
  select(-c(15:18)) %>% #remove youth extra demographic responses
  select(-c(1:10)) %>% #remove embedded demographic data
  select(-c(59:60)) %>% # remove youth written responses
  mutate(Q773 = Q773 %>% str_replace_all(c("Some\r\n" = "Some",
                                  "A lot\r\n" = "A lot",
                                  "Not at all\r\n" = "Not at all",
                                  "Some" = "Some",
                                  "A lot" = "A lot",
                                  "Not at all" = "Not at all")))
d8Y <- d8Y %>% mutate_at(vars(5:58), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Don't Know / Doesn't Relate to Me" = 0,
            )))

colnames(d8Y)[5:58] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
```

```{r}
#CHUNK 9

#Cleaning Parent Responses - one young person
d8F <- d8 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:74)) %>% #remove youth response fields
  select(-c(1:149)) %>% #remove stakeholder response fields
  select(-c(5:8)) %>% #remove write-in demographics and unneeded demographics
  select(-c(9:11,20:22,25:27,32:34,39:41,50:52,60:62,76:78,83:87)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(59:418)) %>% #remove fields for parents responding about more than one young person
  select(-c(59:89)) %>% #remove unneeded embedded data pt 1
  select(-c(62:69)) %>% #remove unneeded embedded data pt 2
  select(-c(63)) %>% #remove unneeded embedded data pt 3
  filter(Q166 == "I want to share about one young person")

d8F <- d8F %>% mutate_at(vars(5:58), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable" = 0,
            )))

colnames(d8F)[5:58] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
d8F$Role <- as.character("I'm a Parent / Legal Guardian")

```

```{r}
#CHUNK 10

#Cleaning Parent Responses - multiple young people
d8Fm <- d8 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:76)) %>% #remove youth response fields
  select(-c(1:149)) %>% #remove stakeholder response fields
  select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics from single youth parents
  select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(131:599)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(135:147)) #remove embedded scores as well as other unneeded embedded fields

d8Fm <- d8Fm %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable" = 0,
            )))

```

```{r}
#CHUNK 11

#Cleaning Stakeholder Responses

d8S <- d8 %>% filter(Role == "I'm a Transition Stakeholder") %>%
  filter(Finished=="True") %>% #only complete response
  select(-c(1:10)) %>% #remove embedded demographic data fields from Qualtrics
  select(-c(2:64)) %>% #remove youth fields
  select(-c(3,4,5,6)) %>% #remove write-in fields and unneeded demo fields for stakeholders
  select(-c(15,16,33,34,45,46,59,60,73,74,91,92,108,109,131,132,145:148)) %>% #remove stakeholder written responses
  select(-c(129:577)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(129:159)) %>% #remove embedded scores as well as other unneeded embedded fields pt 1
  select(-c(132:139)) %>% #remove embedded scores as well as other unneeded embedded fields pt 2
  select(-c(133)) #remove embedded scores as well as other unneeded embedded fields pt 3

d8S <- d8S %>% mutate_at(vars(3:6,15:22,31,32,41:44,53:56,65:72,81:87,96:108,117:120), #re-code all sqi ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=3,
              "Some"=2,
              "Not at all"=1,
              "Not applicable"=0
            )))

colnames(d8S)[3:6] <- c(paste0("SQI",1:4)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[15:22] <- c(paste0("SQI",5:12)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[31:32] <- c(paste0("SQI",13:14)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[41:44] <- c(paste0("SQI",15:18)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[53:56] <- c(paste0("SQI",19:22)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[65:72] <- c(paste0("SQI",23:30)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[81:87] <- c(paste0("SQI",31:37)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[96:108] <- c(paste0("SQI",38:50)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[117:120] <- c(paste0("SQI",51:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.

d8S <- d8S %>% mutate_at(vars(7:9,23:25,33:35,45:47,57:59,73:75,88:90,109:111,121:123,), #re-code all ADAPT ratings from string to numerical
            ~as.numeric(recode(.,
              "Limited Adaptation (2)"=2,
              "Full Adaptation (4)"=4,
              "No Adaptation (1)"=1,
              "Partial Adaptation (3)"=3,
              "Not Applicable"=0
            )))

d8S <- d8S %>% mutate_at(vars(10:12,26:28,36:38,48:50,60:62,76:78,91:93,112:114,124:126), #re-code all ACCESS ratings from string to numerical
            ~as.numeric(recode(.,
              "Limited Access (2)"=2,
              "Full Access (4)"=4,
              "No Access (1)"=1,
              "Partial Access (3)"=3,
              "Not Applicable"=0
            )))

d8S <- d8S %>% select(-c(13,14,29,30,39,40,51,52,63,64,79,80,94,95,115,116,127,128)) #remove resource level and effectiveness ratings. They are not used in the model
d8S <- d8S %>% select(-c(115)) #remove Q168, duplicate field of LEA name
```

```{r}
#CHUNK 12

#union youth, family and stakeholder tables
d8join <- full_join(d8Y,d8F) #youth and families
d8final <- full_join(d8join,d8S) #join with stakeholders
rm(d8join,d8,d8F,d8S,d8Y)

```

Do not find and replace data tables d1 to d11 in the chunk below. It is used for joining all of the site data tables generated by repeating the chunks above.

```{R}
#Join data from all sites
FlanaganFinalData <- full_join(d1final,d2final)
FlanaganFinalData <- full_join(FlanaganFinalData,d3final)
FlanaganFinalData <- full_join(FlanaganFinalData,d4final)
FlanaganFinalData <- full_join(FlanaganFinalData,d5final)
FlanaganFinalData <- full_join(FlanaganFinalData,d6final)
FlanaganFinalData <- full_join(FlanaganFinalData,d7final)
FlanaganFinalData <- full_join(FlanaganFinalData,d8final)
FlanaganFinalData <- full_join(FlanaganFinalData,d9final)
FlanaganFinalData <- full_join(FlanaganFinalData,d10final)
FlanaganFinalData <- full_join(FlanaganFinalData,d11final)
as_tibble(FlanaganFinalData)
print(FlanaganFinalData)

```
