---
title: "Matthew Flanagan - Chapter 4 - Dissertation"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


```{r}
#load packages
library(lavaan)
library(readxl)
library(tidyverse)

#get the TDQI data
d1 <- read_excel("Allentown.xlsx")
d2 <- read_excel("Avon_Grove.xlsx")
d3 <- read_excel("Butler.xlsx")
d4 <- read_excel("Canon_McMillan.xlsx")
d5 <- read_excel("East_Lycoming.xlsx")
d6 <- read_excel("Lebanon.xlsx")
d7 <- read_excel("Mountain_View.xlsx")
d8 <- read_excel("PA_Virtual_Charter.xlsx")
d9 <- read_excel("Plum_Borough.xlsx")
d10 <- read_excel("Southwestern.xlsx")
d11 <- read_excel("Union_Area.xlsx")

```

```{r}
#make a column index for reference, change df as needed to update / modify the index list as cleaning is being completed. Makes de-bugging easier. Not Required. 
column_indexY <- data.frame(colnames(d8Y)) #youth
column_indexF <- data.frame(colnames(d8F)) #parents with 1 young person with a disability
column_indexFm <- data.frame(colnames(d8Fm)) #parents with more than 1 young person with a disability
column_indexS <- data.frame(colnames(d8S)) #transition stakeholders

```


Process d1 through chunks 1 through 6. Then, find and replace "d1" chunks 1 through 6 below. Run the modified chunks to clean each site file EXCEPT for d8, which is a charter. Charter school data is structured slightly different and needs to be cleaned separately. See chunks 7 through 12 for cleaning charter data. Each replacement should be for 51 occurrences. Less or more means there is an error and something was changed.

```{r}
#CHUNK 1

#Rename role, age, gender, school, race
d11 <- d11 %>% rename(Role = Q1) %>% 
  rename(Age = Q2) %>% rename(Gender = Q3) %>% 
  rename(School = Q5) %>% rename(Race_Eth = Q4)

#remove first row acting as question name which was added by Qualtrics out-dated export functionality.
d11 <- d11[-c(1),]
```  

```{r}
#CHUNK 2

#Cleaning Youth Responses
d11Y <- d11 %>% filter(Role =="I'm a Young Person") %>% #filter out just youth responses
  filter(Finished=="True") %>% #only complete responses
  select(-c(77:698)) %>% #remove all fields from the family and stakeholder survey questions
  select(-c(85:93)) %>% #remove unneeded embedded data from Qualtrics
  select(-c(81:84)) %>% #remove unneeded embedded demographic data from Qualtrics. Not accurate. Already have fields.
  select(-c(75:76)) %>% #remove written youth responses
  select (-c(1:10)) %>% #remove embedded survey data from Qualtrics (date, time, etc.)
  mutate(Q773 = Q773 %>% str_replace_all(c("Some\r\n" = "Some",
                                  "A lot\r\n" = "A lot",
                                  "Not at all\r\n" = "Not at all",
                                  "Some" = "Some",
                                  "A lot" = "A lot",
                                  "Not at all" = "Not at all")))
  d11Y <- d11Y %>% select(-c(6:10)) #remove unneeded write-ins for youth demographics
d11Y <- d11Y %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Don't Know / Doesn't Relate to Me" = 1,
            )))

colnames(d11Y)[6:59] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
```

```{r}
#CHUNK 3

#Cleaning Parent Responses - one young person
d11F <- d11 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:76)) %>% #remove youth response fields
  select(-c(1:151)) %>% #remove stakeholder response fields
  select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics
  select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(60:419)) %>% #remove fields for parents responding about more than one young person
  select(-c(60:77)) %>% #remove unneeded embedded data pt 1
  select(-c(64:76)) %>% #remove unneeded embedded data pt 2
  filter(Q166 == "I want to share about one young person")

d11F <- d11F %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Not applicable" = 1,
            )))

colnames(d11F)[6:59] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
d11F$Role <- as.character("I'm a Parent / Legal Guardian")

```

```{r}
#CHUNK 4

#Cleaning Parent Responses - multiple young people
# d11Fm <- d11 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
#   filter(Finished=="True") %>% #only complete responses
#   select(-c(1:76)) %>% #remove youth response fields
#   select(-c(1:151)) %>% #remove stakeholder response fields
#   select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics from single youth parents
#   select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
#   select(-c(1:59)) #remove item fields for single youth parents
# 
# d11Fm <- d11Fm %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
#             ~as.numeric(recode(.,
#               "A lot"=4,
#               "Some"=3,
#               "Not at all"=2,
#               "Not applicable" = 1,
#             )))

```

```{r}
#CHUNK 5

#Cleaning Stakeholder Responses
d11S <- d11 %>% filter(Role == "I'm a Transition Stakeholder") %>%
  filter(Finished=="True") %>% #only complete response
  select(-c(1:10)) %>% #remove embedded demographic data fields from Qualtrics
  select(-c(2:66)) %>% #remove youth fields
  select(-c(3,4,5,8)) %>% #remove write-in fields and unneeded demo fields for stakeholders
  select(-c(17,18,35,36,47,48,61,62,75,76,93,94,110,111,133,134,147:150)) %>% #remove stakeholder written responses
  select(-c(131:599)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(135:147)) #remove embedded scores as well as other unneeded embedded fields

d11S <- d11S %>% mutate_at(vars(5:8,17:24,33,34,43:46,55:58,67:74,83:89,98:110,119:122), #re-code all sqi ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Not applicable"=1,
              "Not Applicable"=1
            )))
colnames(d11S)[5:8] <- c(paste0("SQI",1:4)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[17:24] <- c(paste0("SQI",5:12)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[33:34] <- c(paste0("SQI",13:14)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[43:46] <- c(paste0("SQI",15:18)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[55:58] <- c(paste0("SQI",19:22)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[67:74] <- c(paste0("SQI",23:30)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[83:89] <- c(paste0("SQI",31:37)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[98:110] <- c(paste0("SQI",38:50)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d11S)[119:122] <- c(paste0("SQI",51:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.

d11S <- d11S %>% mutate_at(vars(9:11,25:27,35:37,47:49,59:61,75:77,90:92,111:113,123:125), #re-code all ADAPT ratings from string to numerical
            ~as.numeric(recode(.,
              "Full Adaptation (4)"=5,
              "Partial Adaptation (3)"=4,
              "Limited Adaptation (2)"=3,
              "No Adaptation (1)"=2,
              "Not Applicable"=1,
              "Not applicable"=1
            )))

d11S <- d11S %>% mutate_at(vars(12:14,28:30,38:40,50:52,62:64,78:80,93:95,114:116,126:128), #re-code all ACCESS ratings from string to numerical
            ~as.numeric(recode(.,
              "Full Access (4)"=5,
              "Partial Access (3)"=4,
              "Limited Access (2)"=3,
              "No Access (1)"=2,
              "Not Applicable"=1,
              "Not applicable"=1
            )))

d11S <- d11S %>% select(-c(15,16,31,32,41,42,53,54,65,66,81,82,96,97,117,118,129,130)) #remove resource level and effectiveness ratings. They are not used in the model

```

```{r}
#CHUNK 6

#union youth, family and stakeholder tables
d11join <- full_join(d11Y,d11F) #youth and families
d11final <- full_join(d11join,d11S) #join with stakeholders
rm(d11join,d11,d11F,d11S,d11Y)

```


Chunks 7 through 12 below are used ONLY for cleaning the charter data (d8)

```{r}
#CHUNK 7

#Rename role, age, gender, school, race
d8 <- d8 %>% rename(Role = Q1) %>% 
  rename(Age = Q2) %>% rename(Gender = Q3) %>% 
  rename(School = Q5) %>% rename(Race_Eth = Q4)

#remove first row acting as question name which was added by Qualtrics out-dated export functionality.
d8 <- d8[-c(1),]
```  

```{r}
#CHUNK 8

#Cleaning Youth Responses
d8Y <- d8 %>% filter(Role =="I'm a Young Person") %>% #filter out just youth responses
  filter(Finished=="True") %>% #only complete responses
  select(-c(75:696)) %>% #remove all fields from the family and stakeholder survey questions
  select(-c(75:83)) %>% #remove embedded scores
  select(-c(78:85)) %>% #remove fields relevant to families with more than one young person with a disability pt1
  select(-c(79:80)) %>% #remove fields relevant to families with more than one young person with a disability pt2
  select(-c(15:18)) %>% #remove youth extra demographic responses
  select(-c(1:10)) %>% #remove embedded demographic data
  select(-c(59:60)) %>% # remove youth written responses
  mutate(Q773 = Q773 %>% str_replace_all(c("Some\r\n" = "Some",
                                  "A lot\r\n" = "A lot",
                                  "Not at all\r\n" = "Not at all",
                                  "Some" = "Some",
                                  "A lot" = "A lot",
                                  "Not at all" = "Not at all")))
d8Y <- d8Y %>% mutate_at(vars(5:58), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Don't Know / Doesn't Relate to Me" = 1,
            )))

colnames(d8Y)[5:58] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
```

```{r}
#CHUNK 9

#Cleaning Parent Responses - one young person
d8F <- d8 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:74)) %>% #remove youth response fields
  select(-c(1:149)) %>% #remove stakeholder response fields
  select(-c(5:8)) %>% #remove write-in demographics and unneeded demographics
  select(-c(9:11,20:22,25:27,32:34,39:41,50:52,60:62,76:78,83:87)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(59:418)) %>% #remove fields for parents responding about more than one young person
  select(-c(59:89)) %>% #remove unneeded embedded data pt 1
  select(-c(62:69)) %>% #remove unneeded embedded data pt 2
  select(-c(63)) %>% #remove unneeded embedded data pt 3
  filter(Q166 == "I want to share about one young person")

d8F <- d8F %>% mutate_at(vars(5:58), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Not applicable" = 1,
            )))

colnames(d8F)[5:58] <- c(paste0("SQI",1:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.
d8F$Role <- as.character("I'm a Parent / Legal Guardian")

```

```{r}
#CHUNK 10

#Cleaning Parent Responses - multiple young people
d8Fm <- d8 %>% filter(Role =="I'm a Parent / Legal Guardian") %>%
  filter(Finished=="True") %>% #only complete responses
  select(-c(1:76)) %>% #remove youth response fields
  select(-c(1:149)) %>% #remove stakeholder response fields
  select(-c(6:10)) %>% #remove write-in demographics and unneeded demographics from single youth parents
  select(-c(10:12,21:23,26:28,33:35,40:42,51:53,61:63,77:79,84:88)) %>% #remove effectiveness ratings and written responses from parents.
  select(-c(131:599)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(135:147)) #remove embedded scores as well as other unneeded embedded fields

d8Fm <- d8Fm %>% mutate_at(vars(6:59), #re-code all ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Not applicable" = 1,
            )))

```

```{r}
#CHUNK 11

#Cleaning Stakeholder Responses

d8S <- d8 %>% filter(Role == "I'm a Transition Stakeholder") %>%
  filter(Finished=="True") %>% #only complete response
  select(-c(1:10)) %>% #remove embedded demographic data fields from Qualtrics
  select(-c(2:64)) %>% #remove youth fields
  select(-c(3,4,5,6)) %>% #remove write-in fields and unneeded demo fields for stakeholders
  select(-c(15,16,33,34,45,46,59,60,73,74,91,92,108,109,131,132,145:148)) %>% #remove stakeholder written responses
  select(-c(129:577)) %>% #remove fields relevant to parents responding about more than one young person
  select(-c(129:159)) %>% #remove embedded scores as well as other unneeded embedded fields pt 1
  select(-c(132:139)) %>% #remove embedded scores as well as other unneeded embedded fields pt 2
  select(-c(133)) #remove embedded scores as well as other unneeded embedded fields pt 3

d8S <- d8S %>% mutate_at(vars(3:6,15:22,31,32,41:44,53:56,65:72,81:87,96:108,117:120), #re-code all sqi ratings from string to numerical
            ~as.numeric(recode(.,
              "A lot"=4,
              "Some"=3,
              "Not at all"=2,
              "Not applicable"=1
            )))

colnames(d8S)[3:6] <- c(paste0("SQI",1:4)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[15:22] <- c(paste0("SQI",5:12)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[31:32] <- c(paste0("SQI",13:14)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[41:44] <- c(paste0("SQI",15:18)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[53:56] <- c(paste0("SQI",19:22)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[65:72] <- c(paste0("SQI",23:30)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[81:87] <- c(paste0("SQI",31:37)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[96:108] <- c(paste0("SQI",38:50)) #add SQI to all items measuring a sub-indicator and add the number of the item.
colnames(d8S)[117:120] <- c(paste0("SQI",51:54)) #add SQI to all items measuring a sub-indicator and add the number of the item.

d8S <- d8S %>% mutate_at(vars(7:9,23:25,33:35,45:47,57:59,73:75,88:90,109:111,121:123,), #re-code all ADAPT ratings from string to numerical
            ~as.numeric(recode(.,
              "Full Adaptation (4)"=5,
              "Partial Adaptation (3)"=4,
              "Limited Adaptation (2)"=3,
              "No Adaptation (1)"=2,
              "Not Applicable"=1,
              "Not applicable"=1
            )))

d8S <- d8S %>% mutate_at(vars(10:12,26:28,36:38,48:50,60:62,76:78,91:93,112:114,124:126), #re-code all ACCESS ratings from string to numerical
            ~as.numeric(recode(.,
              "Full Access (4)"=5,
              "Partial Access (3)"=4,
              "Limited Access (2)"=3,
              "No Access (1)"=2,
              "Not Applicable"=1,
              "Not applicable"=1
            )))

d8S <- d8S %>% select(-c(13,14,29,30,39,40,51,52,63,64,79,80,94,95,115,116,127,128)) #remove resource level and effectiveness ratings. They are not used in the model
d8S <- d8S %>% select(-c(115)) #remove Q168, duplicate field of LEA name
```

```{r}
#CHUNK 12

#union youth, family and stakeholder tables
d8join <- full_join(d8Y,d8F) #youth and families
d8final <- full_join(d8join,d8S) #join with stakeholders
rm(d8join,d8,d8F,d8S,d8Y)

```

Do not find and replace data tables d1 to d11 in the chunk below. It is used for joining all of the site data tables generated by repeating the chunks above.

```{R}
#Join data from all sites
FlanaganFinalData <- full_join(d1final,d2final)
FlanaganFinalData <- full_join(FlanaganFinalData,d3final)
FlanaganFinalData <- full_join(FlanaganFinalData,d4final)
FlanaganFinalData <- full_join(FlanaganFinalData,d5final)
FlanaganFinalData <- full_join(FlanaganFinalData,d6final)
FlanaganFinalData <- full_join(FlanaganFinalData,d7final)
FlanaganFinalData <- full_join(FlanaganFinalData,d8final)
FlanaganFinalData <- full_join(FlanaganFinalData,d9final)
FlanaganFinalData <- full_join(FlanaganFinalData,d10final)
FlanaganFinalData <- full_join(FlanaganFinalData,d11final)
FlanaganFinalData$Age <- as.numeric(FlanaganFinalData$Age)
FlanaganFinalData <- rename(FlanaganFinalData,ProfessionalRole = Q65)
as_tibble(FlanaganFinalData)
write.csv(FlanaganFinalData, file = "FlanaganFinalData.csv")

```

```{r}
#get cleaned data if session looses environment
FlanaganFinalData <- read.csv("FlanaganFinalData.csv",header = TRUE)
```

```{r}
#descriptive statistics on sample demographics
library(psych) #turn off before using Lavaan because it masks the covariance matrix functions in Lavaan.
library(ggplot2)

itemstatistics <- describe(select(FlanaganFinalData,c(6:59)))

Role <- ggplot(data=FlanaganFinalData,aes(x=Role)) +
  geom_bar() +
  stat_count(geom="text",
             aes(label = stat(count)))

Gender <- ggplot(data=subset(FlanaganFinalData,!is.na(Gender)),aes(x=Gender)) +
  geom_bar() +
  stat_count(geom="text",
             aes(label = stat(count)))

Age <- ggplot(data=subset(FlanaganFinalData,!is.na(Age)),aes(x=Age)) +
  geom_histogram(binwidth = 1,color="black",fill="white") +
  stat_count(geom="text",
             aes(label=stat(count)))

describe(FlanaganFinalData)

```

```{r}
#subset
all_items <- as_tibble(na.omit((select(FlanaganFinalData,c(7:60)))))
QI2_items <- as_tibble(select(all_items,c(5:12)))
trns_items <- as_tibble(select(all_items,c(1:4,13:54)))
trns_items2 <-as_tibble(select(all_items,c(1:4,13:54)))

itemkey = data.table(
  SQIs = c("Career Exploration Planning and Preparation 1.1",
           "Postsecondary and College Planning 1.2",
           "Independent/Community Living 1.3",
           "Significant Role of School Personnel 1.4",
           "Self-Awareness 2.1",
           "Disability Awareness 2.2",
           "Independent Living Skill Development 2.3",
           "Self-Determination Skill Development 2.4",
           "Self-Management Skill Development 2.5",
           "Leadership Skill Development 2.6",
           "Youth Engagement in Transition 2.7",
           "Significant Role of Adult 2.8",
           "Authentic Person and Family Centered Planning Practices 3.1",
           "Person and Family Centered Program Design 3.2",
           "Family Engagement in Transition Planning 4.1",
           "Family Information Sharing Activities 4.2",
           "Peer to Peer Family Support 4.3",
           "Family Respite 4.4",
           "Friendship 5.1",
           "Sense of Belonging 5.2",
           "Social Skills Development 5.3",
           "Anti-Bullying Efforts 5.4",
           "Independent Living Skills Development 6.1",
           "Planning for Future Living Arrangements 6.2",
           "Travel and Transportation Skills 6.3",
           "Recreation and Leisure 6.4",
           "Community Based Experiences 6.5",
           "Faith Based Experiences 6.6",
           "Civic Engagement 6.7",
           "Mental Health Supports 6.8",
           "Agencies in Schools 7.1",
           "Transition Coordinating Councils 7.2",
           "Community Agency Nights about Employment 7.3",
           "Transition Staffings 7.4",
           "Employment Expos 7.5",
           "Transition Fairs 7.6",
           "Transition Conferences 7.7",
           "Career Development Classes 8.1",
           "Career Clubs 8.2",
           "Career and Technical Education 8.3",
           "Career Exploration 8.4",
           "Discovery Process 8.5",
           "Unpaid Work Experience 8.6",
           "Paid Work Experience 8.7",
           "OVR Services 8.8",
           "Job Coaching Services 8.9",
           "Summer Employment 8.10",
           "On-the-Job Training 8.11",
           "Employer Partnerships 8.12",
           "University Partnerships 8.13",
           "Pre-College Experience Programs 9.1",
           "College-Based Transition Programs 9.2",
           "Postsecondary Education Programs 9.3",
           "Postsecondary Career Training Programs 9.4"
           ),
  Subindicators = c(paste("SQI",1:54))
)

```

```{r}
library(psych)
library(corrplot)
library(polycor) #masks polyserial from pysch package

#Create and plot a correlation matrix of the SQIs
#all items
all_items_correlations <- polychoric(all_items,smooth=TRUE,global=TRUE,weight=NULL,progress=TRUE,na.rm=TRUE, delete=TRUE)
all_items_corrplot <- corrplot(SQIitemcorrelations$rho,type = "lower")

#just QI2
QI2_items_correlations <- polychoric(QI2_items,smooth=TRUE,global=TRUE,weight=NULL,progress=TRUE,na.rm=TRUE, delete=TRUE)
QI2_items_corrplot <- corrplot(QI2_items_correlations$rho,type = "lower",method="number")

#all besides QI2
trns_items_correlations <- polychoric(trns_items,smooth=TRUE,global=TRUE,weight=NULL,progress=TRUE,na.rm=TRUE, delete=TRUE)
trns_items_corrplot <- corrplot(trns_items_correlations$rho,type = "lower",method="number")
```

```{r}
library(dplyr)
library(data.table)
library(ggplot2)
library(FactoMineR)
library(infotheo)

#Feature extraction for "transition planning (trns)" through PCA

#Check factorability of the data
KMO <- KMO(trns_items_correlations$rho)
anticorr <- corrplot(KMO$ImCov,type= "lower",method = "number")
Bart <- cortest.bartlett(all_items_correlations$rho,n=624)

#create total trns score (which is target variable for PCA)
trns_items2$trnsqual <- as.numeric(rowSums(trns_items[,c(1:45)]))

#equal width discretize trnsqual vector to 3 bins representing the ordinal scale of the 46 features
#trnsqual_dis <- discretize(trns_items2$trnsqual,disc="equalwidth",nbins=3)
#trns_items2$trnsqual <- trnsqual_dis$X

#make the target variable null in the forthcoming analyses
#trns_items2 < trns_items2[,trnsqual := NULL]

#run PCA
trns_pca <- prcomp(trns_items2,scale. = FALSE)

#get eigen values from the PCA 
trns_pca$eigenvalues <- trns_pca$sdev^2

#Calculate the percentage of variation within each principal component and plot the results
trns_pca_var <- trns_pca$sdev^2 
trns_pca_var_perc <- round(
  trns_pca_var/sum(trns_pca_var)*100
  ,1)

barplot(trns_pca_var_perc,
        main= "PC Variation Plot",
        xlab="Principal Components",
        ylab="Percentage of Variance", 
        ylim = c(0,100)
        )

#Rotation - assign weights to features in each PCA (loadings), with an array of loadings for each PC being an Eigenvector. Goal is to identify which features are most important in differentiating between the quality of transition planning experiences

PC1 <- trns_pca$rotation[,1]
PC1_scores <- abs(PC1)
PC1_scores_ordered <- sort(PC1_scores,decreasing = TRUE)
names(PC1_scores_ordered)
print(PC1_scores_ordered) #names and scores 
trns_pca_loadings <- as_tibble(print(trns_pca$rotation[,1:6]))

write.csv(trns_pca_loadings,"C:\\Users\\snowb\\Box\\Matt Flanagan's Box Drive\\GW UNIVERSITY, GSEHD\\Dissertation\\Writing\\pcaloadings.csv")
  
#comms
extracted <- sum(trns_pca$eigenvalues)

```

